Digital History in Finland, 1488-1828

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
ok

---
title: "Digital History in Finland, 1488-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "June 22, 2016"
output: markdown_document
---

@@

Aatehistoria ja digitaalisten  aineistojen mahdollisuudet ([Tolonen & Lahti (2015)](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/))

@@

# Figure path
opts_chunk$set(fig.path = "figure_201606_Krakow/")

@@

>>>>

---
title: "Digital History in Finland, 1488-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
bibliography: 
- bibliography.bib
- references.bib
output: 
  md_document:
    variant: markdown_github
---
<!--
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{microbiome tutorial}
  %\usepackage[utf8]{inputenc}
-->

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Handle citations
require(knitcitations)
cleanbib()
#options("citation_format" = "pandoc")
bib <- read.bibtex("bibliography.bib")
#opts_chunk$set(fig.width=4, fig.height=3, par=TRUE, out.width='2in', fig.pos='H')
#knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/", dev="CairoPNG")
knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/")
```

@@

Aatehistoria ja digitaalisten  aineistojen mahdollisuudet ([Tolonen & Lahti (2015)](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/)). Citing with URL `r citep("http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet")`

We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)). Citing with DOI: `r citep("10.18352/lq.10112")`

@@

@@

### References

```{r, echo=FALSE, message=FALSE}
#Embed citations from bib files with `r citep(bib[["lahti14natcomm"]])`. Or with @lahti14natcomm
#You can embed citations, for example: `r citep(bib[["lahti14natcomm"]])`
#You can embed citations, for example2: @lahti14natcomm
#Cite with DOI: `r citep("10.1890/11-0011.1")`
#Cite URL `r citep("http://knowledgeblog.org/greycite")`
#For automated markdown citations, check [this](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html), [this](https://github.com/cboettig/knitcitations), and [this](http://www.carlboettiger.info/2012/03/24/citations-in-markdown-using-knitr.html). 
#write.bibtex(file="references.bib")
```

```{r, echo=FALSE, message=FALSE, results='asis'}
bibliography()
```

### Dependencies

The package utilizes tools from a number of other R extensions,
including dplyr `r citep(citation("dplyr"))`, ggplot2 `r citep(citation("ggplot2"))`, stats `r citep(citation("stats"))`, tidyr `r citep(citation("tidyr"))`.
